---
title: "Analyzing Investments in Analytics"
output: word_document
---

Information about the innovations in analytics business ecosystem is valuable to both established companies as well as startups. Fortunately CrunchBase - the world’s most comprehensive dataset of startup activity,  captures quite a bit of such information 
Founded in 2007 by Mike Arrington, CrunchBase began as a simple crowd sourced database to track startups covered on TechCrunch.  Today you’ll find about 650k profiles of people and companies that are maintained by tens of thousands of contributors.
Venture Capital firms have willingly shared this information so that others could benefit. It's also accessible to everyone as APIs and to researches as downloadable workbook.  

rcrunchbase is an R client to the CrunchBase API (https://developer.crunchbase.com/) developed by Tarak Shah of UC Berkeley. It has several helpful functions that aim to create a compositional query flow. As much as possible, complex queries can be built up from simple requests. The intent is to have rcrunchbase  handle the messy stuff while you focus on getting the data you want.

As an example let's study the investments in analytics in the last 10 years

rcrunchbase can be installed from github.
```{r setup}
install.packages("devtools")
devtools::install_github("tarakc02/rcrunchbase")
library(rcrunchbase)
library(dplyr)
library(stringr)
library(magrittr)
```

## grab a data frame of all of the categories
categories <- crunchbase_get_collection("categories")
 
# find categories that relate to analytics and get related collection:
myCat <- c("Analytics", "Business Analytics", "Big Data Analytics", "Algorithms", "Artificial Intelligence", "Predictive Analytics") 
myCat_uuid<-categories[categories$name %in% myCat, ]$uuid
analytics_orgs <-myCat_uuid %>% crunchbase_get_collection("organizations", category_uuids = .)

analytics<-crunchbase_get_collection("organizations", category_uuids = "2eecf11d5b07d3d2a042643c5025e4ec")


 
# now analytics is a dataframe with names/links to analytics-related companies.
# This list will probably be longer than 2,500 companies, so you’ll need to adjust everything accordingly,
# but hopefully the logic makes sense:
 
analytics_companies <- analytics %>% crunchbase_get_details
investments <- crunchbase_expand_section(analytics_companies, "funding_rounds")
investment_details <- crunchbase_get_details(investments)
 
By the end of that, investment_details will be a list where each member is the details for a particular funding round for a particular company. Each element in the list will include information about the companies involved, the date of the investment, the amount of the investment, etc.. As a very basic example, you could hack together something like this:
 
myfun<- function(x) {
    data.frame(company = x$relationships$funded_organization$items$name,
               date = x$properties$announced_on,
               amount = x$properties$money_raised_usd)}
lapply(investment_details, myfun) %>%
    do.call("rbind", .)
 



```{r, echo=FALSE}
library(rcrunchbase)
library(magrittr)
ra <- crunchbase_get_details("organization/revolution-computing")
ls.str(ra[[1]])
names(ra[[1]])
str(ra[[1]]$relationships)
```

crunchbase_expand_section(ra, "current_team")
crunchbase_expand_section(fb, c("current_team", "past_team"))

These three functions can be combined in diverse ways, resulting in a much richer and more expressive approach to the API. To take full advantage of the compositional nature of these functions, it’s useful to have a “piping” operator to pass results of one function to inputs for the next function. I prefer the %>% operator from the magrittr package.

library(magrittr)

ra_invests <- crunchbase_expand_section(ra, c("current_team", "past_team")) %>%
    crunchbase_get_details %>%
    crunchbase_expand_section("investments")
ra_invests$invested_in.name

fb <- crunchbase_get_details("organization/paypal")
fb_invests <- crunchbase_expand_section(ra, c("current_team", "past_team")) %>%
    crunchbase_get_details %>%
    crunchbase_expand_section("investments")
fb_invests$invested_in.name
x <- crunchbase_get_collection("category/analytics")
